%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Author : [Name] [Surname], Tomas Polasek (template)
% Description : First exercise in the Introduction to Game Development course.
%   It deals with an analysis of a selected title from the point of its genre, 
%   style, and mechanics.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper,10pt,english]{article}

\usepackage[left=2.50cm,right=2.50cm,top=1.50cm,bottom=2.50cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=blue}

\newcommand{\ph}[1]{\textit{[#1]}}

\title{%
Analysis of Mechanics%
}
\author{%
Jan Kubala (xkubal12)%
}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

{%
\large

\begin{itemize}

\item[] \textbf{Title:} Hidden and Dangerous 2: Courage Under Fire

\item[] \textbf{Released:} 2003

\item[] \textbf{Author:} 2K Czech, Gathering of Developers, 2K Play, Take-Two Interactive

\item[] \textbf{Primary Genre:} Tactical shooter

\item[] \textbf{Secondary Genre:} FPS, Stealth, WW2, Squad-based, Multiplayer PvP and coop

\item[] \textbf{Style:} Realistic

\end{itemize}

}

\section*{\centering Analysis}
\subsection*{Reflections of genres in gameplay}
The game strongly emphasizes tactical game-play, especially in the higher difficulties, where even a single enemy poses a considerable threat. This means the player has to carefully plan how to approach the mission and also figure out how to allocate limited resources in form of ammunition, medical supplies, secondary equipment (fence cutters, explosives etc).

All of this is made even more challenging by each soldier having a limited carry capacity and being able to take the equipment only in planning phase at the beginning of a mission, or more usually a campaign, which can consist of several missions.

The player can also control squad mates and switch between them, while also being able to approach the mission in different ways -- stealth, disguise infiltration, or direct combat.

The game offers a variety of PvP game-modes and also an option to team up and complete the campaign missions in coop mode. Most, if not all missions are inspired by real WW2 events, so when paired with the first person view they provide deep immersion, which transports players to the heart of these covert operations.
\subsection*{Interaction between the genres}
Almost all of the sub-genres support the primary genre, because the systems allow for multiple ways to play it. It can not only be played as a third person shooter, but also a hardcore clone of Call of Duty, or even an RTS. This is possible due to different implementations of the game systems (squad management for example). Of course the developers intended some primary way for the game to be played, which is reflected in some approaches providing smoother gaming experience than others. 

The one genre that stands out the most is the PvP. It turns into a run-and-gun shooter, like Call of Duty, which takes away from the original idea of covert operations and tactical approach.

\subsection*{Game style}
The (for that time) realistic style makes sense to be picked for a game that tries to immerse its players into being a British saboteur in WW2. A stylized look could work, but if not executed cautiously, it could undermine the overall tone of the game.
\end{document}
